---
title: "project725"
author: "Sugandh K"
date: "12/1/2020"
output: pdf_document
---

```{r message=FALSE, warning=FALSE}
rm(list = ls(all = TRUE))

#libraries

#loading up libraries
library(data.table)
library(plyr)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(glmnet)
library(knitr)
library(caret)
library(Metrics)
library(foreign)
library(tidyverse)
library(olsrr)#package for backward selection 
library(corrplot)
library(h2o)
```

```{r}
#setwd("C:/Users/sugan/Desktop/725/project/auction")
df <- read.csv("AuctionData.csv", na.strings = ".",stringsAsFactors = F)
```

```{r}
dim(df)
```

```{r}
str(df[,c(1:10, 604)])
```

```{r}
#getting rid of itemnum and vin 
drop <- c("itemnum","vin")
df = df[,!(names(df) %in% drop)]

```



## Exploring some of the most importent variables 

```{r}
ggplot(data=df[!is.na(df$biddy1),], aes(x=biddy1)) +
        geom_histogram(fill="blue", binwidth = 1000) 
        
```

This does make sense as most of the buyers can't buy high priced cars . 


```{r}
summary(df$biddy1)
```

```{r}
unique(df$buyitnow)
```

There are two types of auctions buyitnow and regular auction . In any auction type if car is sold only then seller will get revenue . Hence keeping data of only sold cars. 


```{r}
df <- df[df$sell == 1,]
row.names(df) <- NULL
```


when there is buyitnow option and if (and only if) that car was sold then the revenue will be bookvalue. 

lets first check if there are any cars which have been sold by buitnow auction 

```{r}
buyitcars <- df[(df$buyitnow == 1)& (df$sell == 1),]
```

```{r}
dim(buyitcars)
```

Okay so there is only 1 car which was sold by buyitnow option . so lets replace original dataframes highest bid with bookvalue of this car.


```{r}
buyitcars$bookvalue
```
```{r}
df[31566 , 35]

```
But before replacing it with bookvalue we can see that it already has a bid value. So some seller put his ford for sell with bookvalue option but buyers bid on it and bought it.Hence there is no need of replacing the bid value 



```{r}
summary(df$biddy1)
```

and now there are no null values for highest bid. 


## Data Cleaning 

We have used grouped variables for rust , ding , problem etc. created by author
so there is no need of individual variables associating with them 

```{r}
#names(df)
df <- df[-c(78:413)]
```

```{r}
#names(df)
df <- df[-c(211:259)]
```

```{r}
dim(df)
```
There are many biddernames in the dataset. I am assuming that the name of the bidder doesn't influence the revenue hence I am deleting them. 


```{r}

df <- df[!grepl("^biddername",names(df))]
```

```{r}
dim(df)
```


Dropping columns with high null values. 


```{r}
#colSums(is.na(df))

# #dropping columns with more than 15% missing values
df<- df[ , colSums(is.na(df)) < 6500 ,]
dim(df)
```
### Dropping missing rows 
```{r}


df <- na.omit(df)
dim(df)
```

## Date Variables 

There are many variables associated with dates like week , length , endsunday. There is variable for the week in which auction was placed , so other date variables like starting date and ending date become redundent , so lets just drop them 


The variable member since is interesting as old website users might have more  understanding of auctions. 

```{r}
library(lubridate)
## Dealing with date variables
df$startdate <- parse_date_time(df$startdate, orders="mdy HMS")
df$enddate <- parse_date_time(df$enddate, orders="mdy HMS")
df$membersince <- parse_date_time(df$membersince, orders="mdy")

#extracting year from member since 
df$memberyr <- year(df$membersince)

df$months <-month(df$startdate)
df$days <-day(df$startdate)
df$monthe <-month(df$enddate)
df$daye <-day(df$enddate)
df$wdays <-  wday(df$enddate)

drop <- c("startdate","enddate","membersince")
df = df[,!(names(df) %in% drop)]



```



## The most important Numerical Variables 





```{r}
numvar <- which(sapply(df, is.numeric)) 
numnames <- names(numvar) 
cat('There are', length(numvar), 'numeric variables')
```
We have 74 Numeric Variables lets see their correlation with the highest bid 

```{r}
#dataset of numeric variables 
numdf <- df[,numnames]

#pairwise correlation 
cor_numVar <- cor(numdf, use="pairwise.complete.obs")

#correlation with highest bid
cor_sorted <- as.matrix(sort(cor_numVar[,'biddy1'], decreasing = TRUE))


#highly correlated variables 

CorHigh <- names(which(apply(cor_sorted, 1, function(x) abs(x)>0.1)))

#matrix of high correlated variables 
cor_numVar <- cor_numVar[CorHigh, CorHigh]

options(repr.plot.width=10, repr.plot.height=10)
corrplot(cor_numVar, tl.col="black", tl.pos = "lt", number.cex=0.65,  tl.cex=0.7)

```

As you can see there are many variables which have their log values . So just keep one of them instead of both.


```{r}
drop <- c("logmiles","biddy2","logstart","logbid2", "age2", "descriptionsize","auction")
df = df[,!(names(df) %in% drop)]

dim(df)
```
```{r}
#names(df)
```

Lets see if there are more redundent variables 
X_merge variables just shows the merging of datasets so lets just drop it. 
we have age and logage , so lets drop age. 
the names of seller and bideer generally dont influence the revenue so lets drop them. 
Sellerborn and sellerage is in dataset. lets drop sellerborn from the dataset.
lets keep logtext instead of text. 
lets keep loghtml instead of html. 

```{r}
drop <- c("X_merge","age","highbiddername","sellername","sellerborn",
          "text","html","name","software")
df = df[,!(names(df) %in% drop)]
dim(df)
```

## label Encoding and Factorising variables 


```{r}
unique(df$trans)
df$trans <- as.factor(df$trans)
```
```{r}
unique(df$doors)
df$doors <- as.factor(df$doors)
```


```{r}
#similarly
df$ding_group <- as.factor(df$ding_group)
df$scratch_group <- as.factor(df$scratch_group)
df$crack_group <- as.factor(df$crack_group)
df$broken_group <- as.factor(df$broken_group)
df$dent_group <- as.factor(df$dent_group)
df$problem_group <- as.factor(df$problem_group)
df$rust_group <- as.factor(df$rust_group)

```

### Creating factor variables

```{r}
table(df$model)
```


```{r}

df$model <- as.factor(df$model)

```

```{r}
table(df$interior)
```

looks like there are missing values in interior as --. lets just drp them and make it as factor. 

```{r}
df <- df[df$interior != "--" ,]
```

```{r}
table(df$interior)
```

```{r}
df$interior <- as.factor(df$interior)
```

```{r}
table(df$exterior)
```

```{r}
df$exterior <- as.factor(df$exterior)
```


```{r}
table(df$model)
```

```{r}
df$maker <- as.factor(df$maker)
```

```{r}
table(df$webpage)
```

```{r}
df$webpage <- ifelse(df$webpage=="ebayhosting",1,0)
```


```{r}

df$condition <- ifelse(df$webpage=="Used",1,0)

```

```{r}

extnormcolor <- list("Black", "Blue", "Brown", "Green",
                     "Orange", "Silver", "Tan", "Yellow",
                     "Burgundy","Gold","Gray","Red", "White")

df$exterior <- ifelse(df$exterior %in% extnormcolor,1,0)

intnormcolor <- list("Black","Blue","Brown","Gray",
                     "Gray","Red","Tan","White")

df$interior <- ifelse(df$interior %in% intnormcolor,1,0)

#creating big three 

big3 <- list("Chevrolet","Dodge","Ford")
df$BigThree <- ifelse(df$maker %in% big3, 1,0)

#sports car and others
sportscar <- list("Camaro","Corvette","Mustang","Thunderbird")
midsize <- list("Civic","Accord","Corolla","Camry","Maxima","Altima","3-Series")
truck <- list("F-250","F-150","Tacoma","F-350","Silverado 1500","Silverado 2500","F-100")

df$sportscar <- ifelse(df$model %in% sportscar,1,0)
df$midsize <- ifelse(df$model %in% midsize,1,0)
df$truck <- ifelse(df$model %in% truck,1,0)

```




```{r}

#we will use logbid as revenue as biddy1 is skewed 


```

Lets check if there are any charachter variables 

```{r}
Charcol <- names(df[,sapply(df, is.character)])
Charcol
```
```{r}
unique(df$title)
```
```{r}
df$title <- as.factor(df$title)
```

```{r}
table(df$caradphotos)
```


Carad photos has many missing values so lets just drop it 

```{r}
drop <- c("caradphotos")
df = df[,!(names(df) %in% drop)]
```

```{r}
#table(df$location)
encode_ordinal <- function(x, order = unique(x)) {
  x <- as.numeric(factor(x, levels = order, exclude = NULL))
  x
}
df[["location"]] <- encode_ordinal(df[["location"]])
```



## Correlations again 

```{r}
numvar <- which(sapply(df, is.numeric)) 
numnames <- names(numvar) 
cat('There are', length(numvar), 'numeric variables')

#dataset of numeric variables 
numdf <- df[,numnames]

#pairwise correlation 
cor_numVar <- cor(numdf, use="pairwise.complete.obs")

#correlation with highest bid
cor_sorted <- as.matrix(sort(cor_numVar[,'biddy1'], decreasing = TRUE))


#highly correlated variables 

CorHigh <- names(which(apply(cor_sorted, 1, function(x) abs(x)>0.1)))

#matrix of high correlated variables 
cor_numVar <- cor_numVar[CorHigh, CorHigh]

options(repr.plot.width=10, repr.plot.height=10)
corrplot(cor_numVar, tl.col="black", tl.pos = "lt", number.cex=0.65,  tl.cex=0.7)
```



## Removing outliers 

```{r}
# library(outliers)
# 
# outlier(df$biddy1)


```

```{r}
#dropping the outlier 

df <- df[df$biddy1 < 860100 ,]
```

## Hot encoding factor variables 

```{r}
factvar <- which(sapply(df, is.factor)) 
factnames <- names(factvar) 


factdf <- df[,factnames]
```

```{r}
numvar <- which(sapply(df, is.numeric)) 
numnames <- names(numvar) 


numdf <- df[,numnames]
```


```{r}
#Creating dataset for k-means clustering first 
#Combing two datasets to make final dataset 
finaldata2 <- cbind(numdf, factdf)

```


```{r}
library(stargazer)

#stargazer(finaldata2, type = "latex" )
```




```{r}
drop <- c("model","maker")
factdf= factdf[,!(names(factdf) %in% drop)]
```


#one hot encoding 
```{r}
install.packages('mltools')
library(mltools)


factdf <- one_hot(as.data.table(factdf))

```



```{r}

#Combing two datasets to make final dataset 
finaldata <- cbind(numdf, factdf)
```

```{r}
drop <- c("biddy1","model")
finaldata= finaldata[,!(names(finaldata) %in% drop)]
```

### Choosing dependent variable 

As biddy1 is right skewed we will use log bid as a dependent variable 



```{r}

names(finaldata)[names(finaldata) == "logbid1"] <- "revenue"
#making revenue as first column 
finaldata<- finaldata %>% select(revenue, everything())
names(finaldata) <- make.names(names(finaldata))
```
relationship between revenue and time
```{r}
df1<-finaldata2[, c("biddy1" ,"months" , "monthe", "days" , "daye" )]
dfmonth2 <- df1[df1$monthe == 2,]
meanmonth2 <- mean(dfmonth2$biddy1)
summonth2 <- sum(dfmonth2$biddy1)
meanmonth2
summonth2
dfmonth3 <- df1[df1$monthe == 3,]
meanmonth3 <- mean(dfmonth3$biddy1)
summonth3 <- sum(dfmonth3$biddy1)
meanmonth3
summonth3
dfmonth4 <- df1[df1$monthe == 4,]
meanmonth4 <- mean(dfmonth4$biddy1)
summonth4 <- sum(dfmonth4$biddy1)
meanmonth4
summonth4
dfmonth5 <- df1[df1$monthe == 5,]
meanmonth5 <- mean(dfmonth5$biddy1)
summonth5 <- sum(dfmonth5$biddy1)
meanmonth5
summonth5
dfmonth6 <- df1[df1$monthe == 6,]
meanmonth6 <- mean(dfmonth6$biddy1)
summonth6 <- sum(dfmonth6$biddy1)
meanmonth6
summonth6
dfmonth7 <- df1[df1$monthe == 7,]
meanmonth7 <- mean(dfmonth7$biddy1)
summonth7 <- sum(dfmonth7$biddy1)
meanmonth7
summonth7
dfmonth8 <- df1[df1$monthe == 8,]
meanmonth8 <- mean(dfmonth8$biddy1)
summonth8 <- sum(dfmonth8$biddy1)
meanmonth8
summonth8
dfmonth9 <- df1[df1$monthe == 9,]
meanmonth9 <- mean(dfmonth9$biddy1)
summonth9 <- sum(dfmonth9$biddy1)
meanmonth9
summonth9
dfmonth10 <- df1[df1$monthe == 10,]
meanmonth10 <- mean(dfmonth10$biddy1)
summonth10 <- sum(dfmonth10$biddy1)
meanmonth10
summonth10
#summary monthly mean
monthe <- c(2,3,4,5,6,7,8,9,10)
mean <- c(meanmonth2,meanmonth3,meanmonth4,meanmonth5,meanmonth6,meanmonth7,meanmonth8,meanmonth9,meanmonth10)
#summary monthly sum
sum <- c(summonth2,summonth3,summonth4,summonth5,summonth6,summonth7,summonth8,summonth9,summonth10)
monthly <- data.frame(monthe,mean,sum)
monthly
```
```{r}
#graphically biddy1's mean by month
monthly <- tibble(
  month = c("2","3","4","5","6","7","8","9","10"),
  mean = c(monthly$mean)
)
knitr::kable(monthly)
p3 <- ggplot(data = monthly, mapping = aes(
  x = fct_reorder(month, desc(mean)),
  y = mean ))
p3 + geom_col(fill = "lightblue") +
  geom_text(mapping = aes(
    y = mean / 2, label = paste(mean))) +
  scale_y_continuous(breaks = NULL) +
  coord_flip() + 
  labs(x = "month", 
       y = "mean")
```
```{r}
#summary by days
df1$daye<- as.numeric(df1$daye)
dfmonth_b <- df1[df1$daye <= 10,]
meanmonth_b <- mean(dfmonth_b$biddy1)
summonth_b <- sum(dfmonth_b$biddy1)
meanmonth_b
summonth_b
dfmonth_m <- df1[df1$daye >=11 & df1$daye <= 20,]
meanmonth_m <- mean(dfmonth_m$biddy1)
summonth_m <- sum(dfmonth_m$biddy1)
meanmonth_m
summonth_m
dfmonth_e <- df1[df1$daye >= 21 & df1$daye <= 31,]
meanmonth_e <- mean(dfmonth_e$biddy1)
summonth_e <- sum(dfmonth_e$biddy1)
meanmonth_e
summonth_e
#summary mean
period <- c("Beginning of month","Middle of month","Ending of month")
meandays <- c(meanmonth_b,meanmonth_m,meanmonth_e)
#summary sum
sumdays <- c(summonth_b,summonth_m,summonth_e)
daily <- data.frame(period,meandays,sumdays)
daily
daily <- data.table(daily)
```
```{r}
df4 <-df[, c("biddy1"  , "wdays")]
df4$wdays <- as.numeric(df4$wdays)
dfweekday <- df4[df4$wdays <= 5,]
meanweekday <- mean(dfweekday$biddy1)
meanweekday
dfweekend <- df4[df4$wdays > 5,]
meanweekend <- mean(dfweekend$biddy1)
meanweekend

```
```{r}
#graphically weekdays vs. weekend
wdays <- c("weekday","weekend")
meanwdays <- c(meanweekday,meanweekend)
weekly <- data.frame(wdays,meanwdays)
weekly
weekly <- data.table(weekly)
```
```{r}
dfmon <- df4[df4$wdays == 1,]
meanmon <- mean(dfmon$biddy1)
meanmon
dftue <- df4[df4$wdays == 2,]
meantue <- mean(dftue$biddy1)
meantue
dfwed <- df4[df4$wdays == 3,]
meanwed <- mean(dfwed$biddy1)
meanwed
dfthur <- df4[df4$wdays == 4,]
meanthur <- mean(dfthur$biddy1)
meanthur
dffri <- df4[df4$wdays == 5,]
meanfri <- mean(dffri$biddy1)
meanfri
dfsat <- df4[df4$wdays == 6,]
meansat <- mean(dfsat$biddy1)
meansat
dfsun <- df4[df4$wdays == 7,]
meansun <- mean(dfsun$biddy1)
meansun

```
```{r}
weeks <- c('Monday','Tuesday','Wednesday','Thurday','Friday','Saturday',"Sunday")
meanweeks <- c(meanmon,meantue,meanwed,meanthur,meanfri,meansat,meansun)
week <- data.frame(weeks,meanweeks)
week
week <- data.table(weekly)
```

## Lasso and Ridge 

```{r}
set.seed(0)
sample_size = floor(0.5*nrow(finaldata))


# randomly split data in r
picked = sample(seq_len(nrow(finaldata)),size = sample_size)
train = finaldata[picked,]
test = finaldata[-picked,]
```


```{r}
trainx = train[,!(names(train) %in% "revenue")]
trainy = train[,(names(train) %in% "revenue")]

testx = test[,!(names(test) %in% "revenue")]
testy = test[,(names(test) %in% "revenue")]


set.seed(2020)
my_control <-trainControl(method="cv", number=10)
lassoGrid <- expand.grid(alpha = 1, lambda = seq(0.001,0.1,by = 0.0005))
lasso_mod <- train(x=trainx, y=trainy, method='glmnet', trControl= my_control, tuneGrid=lassoGrid) 




lasso_mse<- mean((testy - predict(lasso_mod, newdata=testx))^2)
lasso_rmse <- sqrt(lasso_mse)



my_control <-trainControl(method="cv", number=10)
ridgeGrid <- expand.grid(alpha = 0, lambda = seq(0.001,0.1,by = 0.0005))

ridge_mod <- train(x=trainx, y=trainy, method='glmnet', trControl= my_control, tuneGrid=ridgeGrid) 



ridge_mse <- mean((testy - predict(ridge_mod, newdata=testx))^2)
ridge_rmse <- sqrt(ridge_mse)

print(paste("Lasso RMSE for only sold cars data is", lasso_rmse))
print(paste("Ridge RMSE for only sold cars data  data is", ridge_rmse))

```

```{r}

lassoVarImp <- varImp(lasso_mod,scale=F)
lassoImportance <- lassoVarImp$importance

varsSelected <- length(which(lassoImportance$Overall!=0))
varsNotSelected <- length(which(lassoImportance$Overall==0))

cat('Lasso uses', varsSelected, 'variables in its model, and did not select', varsNotSelected, 'variables.')

```

## Random forest

Runtime 15 - 20 minutes 

```{r}
set.seed(0)
h2o.init()
#train data as h20 train 
h2o.train=as.h2o(train)
#test data as h20 test 
h2o.test=as.h2o(test)
```


```{r}

#runtime 3-8 minutes
#Random Forest  model for sell data
rf_mod= h2o.randomForest(x=2:501,y=1,
                                training_frame=h2o.train,
                                validation_frame = h2o.test, 
                                model_id = "rf_covType_v1", nfolds = 10,
                                ntrees = 1000, stopping_rounds = 2,  
                                score_each_iteration = T , seed = 121)
```

```{r}
rf_rmse=h2o.rmse(rf_mod)

print(paste("Random Forest  RMSE  is", rf_rmse))
```


```{r}
var2<-h2o.varimp(rf_mod)

var2 
```




```{r}
library(knitr)
library(kableExtra)
library(magrittr)
library(magick)
#webshot::install_phantomjs()
```


```{r}
covars = c("variable" ,"scaled_importance")

var2 <- var2[,covars]
var20 <-head(var2 , 10)

var20$scaled_importance = round(var20$scaled_importance,2)

names(var20)[names(var20) == "scaled_importance"] <- "Importance"
names(var20)[names(var20) == "variable"] <- "Variable"
kable(var20)
```

```{r}
#round the rmse values first 
rf <- round(rf_rmse,digits=3)
ri <- round(ridge_rmse,digits=3)
la <- round(lasso_rmse,digits=3)

library(knitr)
Model <- c("Ridge", "Lasso", "Random Forest" )

RMSE <- c(ri,la, rf  )
msetable <- data.frame(cbind(Model,RMSE))


kable(msetable)
```

##  NRMSE for models 

```{r}
rf_nrmse<-rf_rmse/sd(test$revenue)
la_nrmse <- lasso_rmse/sd(test$revenue)
ri_nrmse <- ridge_rmse/sd(test$revenue)

rf2 <- round(rf_nrmse,digits=3)
ri2 <- round(ri_nrmse,digits=3)
la2 <- round(la_nrmse,digits=3)


```

```{r}
Model <- c("Ridge", "Lasso", "Random Forest" )

NRMSE <- c(ri2,la2, rf2  )
msetable2 <- data.frame(cbind(Model,NRMSE))


kable(msetable2)
```




```{r}
keep <- c("revenue","miles","startbid","n","numbids","year","photos","length","months")
finalpdp = finaldata[,(names(finaldata) %in% keep)]

finalpdp<- finalpdp %>% select(revenue, everything())
```

```{r}
set.seed(0)
sample_size = floor(0.7*nrow(finalpdp))


# randomly split data in r
picked = sample(seq_len(nrow(finalpdp)),size = sample_size)
train3 = finalpdp[picked,]
test3 = finalpdp[-picked,]
```

```{r}
#train data as h20 train 
h2o.train3=as.h2o(train3)
#test data as h20 test 
h2o.test3=as.h2o(test3)
```

```{r}
#Random Forest model 
rffpdp= h2o.randomForest(x=2:9,y=1,
                                training_frame=h2o.train3,
                                validation_frame = h2o.test3, 
                                model_id = "rf_covType_v1",
                                ntrees = 1000, stopping_rounds = 2,  
                                score_each_iteration = T, seed = 2020)
```


```{r}
h2o.rmse(rffpdp)
```






```{r}
pdps <- h2o.partialPlot(rffpdp, h2o.test3, cols =  "year", nbins = 150, plot = F)
pdps2 <- h2o.partialPlot(rffpdp, h2o.test3, cols =  "numbids", nbins = 100, plot = F)
pdps3 <- h2o.partialPlot(rffpdp, h2o.test3, cols =  "n", nbins = 100 , plot = F)
names(pdps3)[names(pdps3) == "n"] <- "num_bidders"
pdps4 <- h2o.partialPlot(rffpdp, h2o.test3, cols =  "miles", nbins = 100 , plot = F)
pdps5 <- h2o.partialPlot(rffpdp, h2o.test3, cols =  "startbid", nbins = 100, plot = F)
pdps6 <- h2o.partialPlot(rffpdp, h2o.test3, cols =  "photos", nbins = 100, plot = F)
pdps7<- h2o.partialPlot(rffpdp, h2o.test3, cols = "length", nbins = 100, plot = F)
pdps8<- h2o.partialPlot(rffpdp, h2o.test3, cols = "months", nbins = 100, plot = F)
```

```{r}
library(ggridges)
library(cowplot)
library(svglite)
options(scipen=10000)
options(repr.plot.width=18, repr.plot.height=8) #plot size
p <- ggplot(data = pdps, aes(x = year, y = mean_response)) +
      geom_line(color = 'red') + geom_point(color = 'red',size=1) + xlab("Year") + ylab("Prediction") +
      theme_minimal()
p2 <- ggplot(data = pdps2, aes(x = numbids, y = mean_response)) +
      geom_line(color = 'red')+ geom_point(color = 'red',size=1) +  xlab("Number of Bids") + ylab("Prediction") +
      theme_minimal()
p3 <- ggplot(data = pdps3, aes(x = num_bidders, y = mean_response)) +
      geom_line(color = 'red')+ geom_point(color = 'red',size=1) +  xlab("Number of Bidders") + ylab("Prediction")+
      theme_minimal()
p4 <- ggplot(data = pdps4, aes(x = miles, y = mean_response)) +
      geom_line(color="red")+ geom_point(color = 'red',size=1) +  xlab("Miles") + ylab("Prediction")+
      theme_minimal()

plot_grid(p,p2,p3,p4, nrow=2, ncol=2)
```

```{r}

p5 <- ggplot(data = pdps5, aes(x = startbid, y = mean_response)) +
      geom_line(color = 'red')+ geom_point(color = 'red',size=1) +  xlab("Starting bid") + ylab("Prediction") +
      theme_minimal()
p6 <- ggplot(data = pdps6, aes(x = photos, y = mean_response)) +
      geom_line(color = 'red')+ geom_point(color = 'red',size=1) +  xlab("Number of Photos") + ylab("Prediction") +
      theme_minimal()
p7 <- ggplot(data = pdps7, aes(x = length, y = mean_response)) +
      geom_line(color = 'red')+ geom_point(color = 'red',size=1) +  xlab("Length of the auction") + ylab("Prediction") +
      theme_minimal()
p8 <- ggplot(data = pdps8, aes(x = months, y = mean_response)) +
      geom_line(color = 'red')+ geom_point(color = 'red',size=1) +  xlab("month of auction") + ylab("Prediction") +
      theme_minimal()

plot_grid(p5,p6,p7,p8, nrow=2, ncol=2)
```


### Most observed model

```{r}
table(finaldata2$model)
```

```{r}
mdata <- finaldata2[, c("model","biddy1","numbids")]
```

```{r}
mdata2<-mdata %>% 
  group_by(model) %>% 
  summarise(observations = n(),
            avg_revenue = mean(biddy1 ),
            avg_bids = mean(numbids)
            )
```
```{r}
mdata2 <-mdata2[order(-mdata2$observations),]
```

```{r}

mdata2$avg_revenue <- round(mdata2$avg_revenue,digits=2)
mdata2
#stargazer(mdata2, summary=FALSE, rownames=TRUE)
```

## K means clustering

finaldata 2 for clustering



```{r}
models <- finaldata2[,c("model","biddy1")]
```
```{r}
models<-models %>% 
  group_by(model) %>% 
  summarise(observations = n(),
            avg_revenue = mean(biddy1)
            )
```

```{r}
models <- models[order(-models$observations ),]
```


```{r}
#stargazer(models , summary = FALSE)
```


```{r}
library(psych)
library(factoextra)
```


```{r}

finaldata2$start <- df$startbid

finalcldata <- finaldata2[df$model == "Mustang" ,]
```


```{r}
numer <- finalcldata[,sapply(finalcldata, is.numeric)]
numer <- numer[, c("logbid1","year","miles","start","n","warranty",
                   "numbids","options")]

names(numer)[names(numer) == "logbid1"] <- "revenue"



invisible(numers <- scale(numer))

fviz_nbclust(numers, kmeans, method = "wss", k.max = 20)





```



```{r}
cluster1 <- kmeans(numers, centers = 6)

c<-aggregate(numer, by=list(cluster=cluster1$cluster), mean)
```

```{r}
head(c)
```


## Demi and Ryan  draw graphs here. Use finaldata2 for graphs.

```{r}

```





### End
