---
title: "Vikrant task"
author: "Vikrant Vilas Kamble"
date: "11/19/2020"
output: 
  
  pdf_document: default
  html_document: defaults 
  word_document: default
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)

library(data.table)
library(rlang)
suppressMessages(library(dplyr))  # I am using the "dplyr" package.
library(ggplot2)
library(leaps)
suppressMessages(library(glmnet))
suppressMessages(library(data.table))
library(foreign)
library(caret)
library(Metrics)
library(tinytex)
library("dplyr")
library("tidyverse")
require("glmnet")
library("glmnet")
```


\ First import the dataset. 
```{r}
#loading a dataset

df <- read.dta("ebaydatafinal.dta")
#DV: revenue:-biddy1,
#Indep VAR:numbids
```

\ Keep only required columns here only dependent variable and independent variable.
```{r}
#keep only dependent and indep. vars
df1 <- df[, c("biddy1", "numbids")]
```


\ See if there are missing values. If, then remove it.
```{r}
colSums(is.na(df1))

```
```{r}
df1 <- na.omit(df1)
```
Now, missing values are removed, check if there are still NA. If not then good to go for relationship/correlation graphs.
```{r}
colSums(is.na(df1))
```
\ make bar plot of ranges for variable numbids. Can do counter plot or see.
\ first check the correlation test between DV and IdV.

```{r}
cr <- cor(df1)
cr
```
\ We can see above the correlation is a bit low which is 0.005, meaning revenue is little related with the number of bidders.

```{r}
library(corrplot)
corrplot(cr, method="number")
```
\ above graph is shows that the relationship between the DV and IV is weak as the color seems white from the color scale.
\ Now lets try to graph the basic relationship using scatter plot.

```{r}
plot(df1$biddy1, df1$numbids, xlab="Revenue", ylab="Number of Bidders", main="Relationship between revenue and no. of bidders")
```

\ Just limit the x and y axis scale and see what happen
```{r}
plot(df1$biddy1, df1$numbids, xlab="Revenue", ylab="Number of Bidders", main="Relationship between revenue and no. of bidders", xlim=c(0,500000), ylim=c(0,200), pch=20)
```
\ Again limit the x and y axis scale to get more info.

```{r}
plot(df1$biddy1, df1$numbids, xlab="Revenue", ylab="Number of Bidders", main="Relationship between revenue and no. of bidders", xlim=c(0,300000), ylim=c(0,200), pch=20, col="green")
```
\ Now do some bar graphs. \
See the frequesncy of the number of bids
```{r}
freqbids.freq <- table(df1$numbids)
barplot(freqbids.freq, xlab="Number of Bidders", main="Frequeancy for no. of bidders")
```
```{r}
col<- c(rep("red", 5), rgb(59, 89, 152, maxColorValue = 255))
```


```{r}
barplot(freqbids.freq[order(freqbids.freq, decreasing=T)], col=col , xlab="Number of Bidders", main="Frequeancy for no. of bidders")
```
```{r}
barplot(freqbids.freq[order(freqbids.freq)], horiz=T, xlab="Number of Bidders", main="Frequeancy for no. of bidders")
```


Now check the frequesncy for the revenue
```{r}
freqRev.freq <- table(df1$biddy1)
barplot(freqRev.freq, col=col , xlab="Revenue", main="Frequeancy for Revenue")
```
\ Now covert the numbids(cont. var) into some categories
```{r}
is.numeric(df1$numbids)
```
\ Now let's try by the number of cut to the number of bids.
```{r}
df2 <- cut(df1$numbids, br=c(-1, 100, 200, 300, 400, 500), labels = c("between0to100", "between100to200", "between200to300", "between300to400", "between400to500"))
#df2 #created the 5 levels (-1,100] (100,200] (200,300] ... (400,500]
```
\ check for surely is new dataframe is still numeric
```{r}
is.numeric(df2)
```
```{r}
is.factor(df2)
```
\ OKay, now good to go.
\ let's check frequency
```{r}
table(df2)
```


\ If we want the R to cut the numebric observations into numbers of categories we want then do this...
```{r}
df3 = cut(df1$numbids, 3) #where 3 is number of cuts we want
#df3
table(df3)
```


\ Now run a simple regressio of revenue on number of bidders
```{r}
mod1 <- lm(biddy1~ numbids, data=df1)
mod1
```
\ Now just do regresssion conditional on the removing outliers from the numbids.
```{r}
mod2 <- lm(biddy1~ numbids, data=subset(df1, numbids>80))
mod2
```
\ When we do remove the outliers then estimate is getting good.










